---
title: "R Notebook"
output: html_notebook
---

loading the dataset

```{r}
install.packages("readxl")
library(readxl)
# Replace "path/to/your/file.xlsx" with the actual file path
data <- read_excel("~/Downloads/mudkip_ftw.xlsx", sheet = "Sheet1")
head(data)
colnames(data)


```

```{r}
install.packages("ggplot2")
library(ggplot2)
```

```{r}

ggplot(data, aes(x = playtime_hours, fill = group)) + 
  geom_histogram(alpha = 0.5, position = "identity", bins = 20) +
  theme_minimal() + 
  labs(title = "Distribution of Playtime Hours by Starter Group", x = "Playtime Hours", y = "Frequency")


```

```{r}
# Histogram for satisfaction_rating by group
ggplot(data, aes(x = satisfaction_rating, fill = group)) + 
  geom_histogram(alpha = 0.5, position = "identity", bins = 20) +
  theme_minimal() + 
  labs(title = "Distribution of Satisfaction Rating by Starter Group", x = "Satisfaction Rating", y = "Frequency")
```

shpiro-wilk test to be sure its normal (has to be on numeric data)

```{r}
# shapir-Wilk test for group A
# Shapiro-Wilk test for playtime_hours
shapiro_playtime <- shapiro.test(data$playtime_hours)
print(shapiro_playtime)

# Shapiro-Wilk test for satisfaction_rating
shapiro_satisfaction <- shapiro.test(data$satisfaction_rating)
print(shapiro_satisfaction)

```

```{r}
# Load the necessary library
library(ggplot2)

# Histogram for Playtime Hours
ggplot(data, aes(x = playtime_hours)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Playtime Hours", x = "Playtime Hours", y = "Frequency") +
  theme_minimal()

# Histogram for Satisfaction Rating
ggplot(data, aes(x = satisfaction_rating)) +
  geom_histogram(binwidth = 0.5, fill = "lightgreen", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Satisfaction Rating", x = "Satisfaction Rating", y = "Frequency") +
  theme_minimal()

```

```{r}
# Q-Q plot for Playtime Hours
qqnorm(data$playtime_hours, main = "Q-Q Plot for Playtime Hours")
qqline(data$playtime_hours, col = "red")

# Q-Q plot for Satisfaction Rating
qqnorm(data$satisfaction_rating, main = "Q-Q Plot for Satisfaction Rating")
qqline(data$satisfaction_rating, col = "red")

```

its significant so its not normal, running **non-parametric tests** that do not rely on the assumption of normality.

```{r}
# Kruskal-Wallis test for playtime_hours across groups
kruskal_playtime <- kruskal.test(playtime_hours ~ group, data = data)
print(kruskal_playtime)

# Kruskal-Wallis test for satisfaction_rating across groups
kruskal_satisfaction <- kruskal.test(satisfaction_rating ~ group, data = data)
print(kruskal_satisfaction)

```

```{r}
# Boxplot for Playtime Hours across groups
ggplot(data, aes(x = group, y = playtime_hours, fill = group)) +
  geom_boxplot() +
  labs(title = "Boxplot of Playtime Hours by Group", x = "Group", y = "Playtime Hours") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set3") # You can change the color palette if desired

```

```{r}
# Boxplot for Satisfaction Rating across groups
ggplot(data, aes(x = group, y = satisfaction_rating, fill = group)) +
  geom_boxplot() +
  labs(title = "Boxplot of Satisfaction Rating by Group", x = "Group", y = "Satisfaction Rating") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set3") # Again, customize color palette if preferred

```

The null hypothesis for the test is that the distribution of the variable is the same across all groups. If the p-value is less than 0.05, you can reject the null hypothesis, indicating a significant difference between the groups.

post hoc test :\
Pairwise MWU tests with Bonferroni Correction or Holm-Bonferroni Correction (unpaired)

```{r}
# Install the 'dunn.test' package for the post-hoc pairwise Wilcoxon test
install.packages("dunn.test")
library(dunn.test)
```

```{r}
library(dunn.test)
# Perform Dunn's Test for playtime_hours across groups
dunn_playtime <- dunn.test(data$playtime_hours, data$group, kw = TRUE, label = TRUE, list = TRUE)
print(dunn_playtime)

# Perform Dunn's Test for satisfaction_rating across groups
dunn_satisfaction <- dunn.test(data$satisfaction_rating, data$group, kw = TRUE, label = TRUE, list = TRUE)
print(dunn_satisfaction)

```

```{r}
# Load necessary library
library(ggplot2)

# Boxplot for Playtime Hours by Group
ggplot(data, aes(x = group, y = playtime_hours, fill = group)) + 
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Playtime Hours by Starter Pokémon", 
       x = "Starter Pokémon", 
       y = "Playtime (hours)") +
  scale_fill_brewer(palette = "Set2")


```

```{r}
# Boxplot for Satisfaction Rating by Group
ggplot(data, aes(x = group, y = satisfaction_rating, fill = group)) + 
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Satisfaction Rating by Starter Pokémon", 
       x = "Starter Pokémon", 
       y = "Satisfaction Rating (1-7)") +
  scale_fill_brewer(palette = "Set2")
```

-   

    **For Playtime Hours**:

    There are significant differences between the groups **Mudkip**, **Torchic**, and **Treecko** for **playtime hours**. Specifically, **Mudkip** is significantly different from both **Torchic** and **Treecko** in terms of playtime, while there is no significant difference between **Torchic** and **Treecko**.

    **For Satisfaction Rating**:

    There are significant differences in **satisfaction ratings** between **Mudkip** and **Treecko**, as well as **Torchic** and **Treecko**. However, **Mudkip** and **Torchic** do not show a significant difference in satisfaction ratings.
